Life in the canopy: Phylogenetic filtering and morphological canalization in epiphytic ferns

### 2019-07-18 ms/manuscript.Rmd
Use pearson's correlation to subset climatic vars and AIC to choose climate models

We calculated mean daily maximum, mean, minimum, and standard variation of temperature and RH from the raw climate data, then tested for differences in these summary statistics between epiphytic and terrestrial dataloggers using ANCOVA [@Scheffers2013]. We used daily mean values of temperature and RH each in turn as the response variable, and constructed linear models with growth habit as the factor and elevation as the covariate, and with their interaction to test for differences in response of climatic variables to elevation between epiphytic and terrestrial dataloggers. We also calculated the number of drying events at various minimum RH values, as well as daily mean values for water potential, but found that these were both highly correlated with mean RH and did not analyze them further (data not shown).

>>>>

We calculated mean daily mean, minimum, and standard variation of temperature and RH for each site from the raw climate data, then grand means from the daily means. We analyzed correlation between the grand means with Pearson's correlation coefficient, and retained a set with correlation coefficients less than 0.9 (hereafter, "climatic variables"). We constructed models to test for differences in response of climatic variables to elevation between epiphytic and terrestrial dataloggers. For each retained climatic variable, we constructed three linear models: one with growth habit (epiphytic vs. terrestrial) only, one with elevation only, and one with the interaction of elevation and growth habit. We compared the fit of the models using the Akaike Information Criteron (AIC) [@Akaike1973], and kept the model with the smallest AIC for each climatic variable. A single outlier site located on an exposed south-facing slope with unusually high temperature and low humidity (Mt. Rotui, 830 m) site was excluded from analysis.
